\documentclass[letterpaper,10pt]{article}

\usepackage{xcolor}
\usepackage{hyperref}
\usepackage{tabularx}
\usepackage{geometry}

\geometry{left=1in,right=1in,top=0.8in,bottom=0.8in}
\hypersetup{hidelinks}
\setlength{\parskip}{0pt}
\setlength\parindent{0pt}

\renewcommand{\labelitemii}{$\circ$}
\newcommand{\listparam}{
    \setlength{\parsep}{\parskip}
    \setlength{\itemsep}{0.2ex}
    \setlength{\labelwidth}{2em}
    \setlength{\labelsep}{1em}
    \setlength{\topsep}{0pt}
    \setlength{\partopsep}{0.2ex}
    \setlength{\leftmargin}{2em}
}

\newcommand{\sublistparam}{
    \setlength{\parsep}{\parskip}
    \setlength{\itemsep}{0.2ex}
    \setlength{\labelwidth}{2em}
    \setlength{\labelsep}{0.5em}
    \setlength{\topsep}{0pt}
    \setlength{\partopsep}{0.2ex}
    \setlength{\leftmargin}{1em}
}

\pagestyle{empty}

\renewcommand{\section}[1]{\vspace{4pt}{\large\textbf{#1}}\vspace{1pt}\hrule\vspace{2pt}}
\renewcommand{\subsection}[1]{\vspace{1pt}{#1}}

\definecolor{mygray}{gray}{0.93}

\usepackage{helvet}
\renewcommand{\familydefault}{\sfdefault}

\begin{document}

\begin{center}
\textbf{\LARGE{Xuanyi Li}}

{\small
$\diamond$~614-397-8198~~$\diamond$~\href{mailto:wirybeaver@outlook.com}{wirybeaver@outlook.com}~~
$\diamond$~\href{https://www.linkedin.com/in/wirybeaver}{linkedin.com/in/wirybeaver}~~
$\diamond$~\href{https://shanelxy.top/portfolio}{shanelxy.top/portfolio}
}
\end{center}

\vspace{-8pt}
\section{EDUCATION}

\subsection{\textbf{The Ohio State University\hfill{Columbus, United States}}}

{\small Master of Science in Computer Science; GPA (3.97/4.0)}\hfill{{\small 08/2017 -- 05/2019}}

\subsection{\textbf{Zhejiang University\hfill{Hangzhou, China}}}

{\small Bachelor of Engineering in Automation; GPA (3.97/4.0); Ranking (4/144)}\hfill{{\small 09/2013 -- 07/2017}}

\section{TECHNICAL SKILLS}

\textbf{Programming Language:} Java, C, GO, Python, SQL, X86 Assembly

\textbf{Framework:} Spring Boot, Apache Druid, gRPC, Apache Kafka, Redis, Keras, Mybatis

\textbf{Operation:} JUnit, Mockito, Git, Gradle, Jenkins, Docker, Terraform,  AWS(EC2, S3)

\section{WORK EXPERIENCE}

\subsection{\textbf{Software Engineer}\hfill{\textbf{Quantcast, Seattle}}}

{\small\textsl{Audience Platform}}\hfill{{\small 07/15/2019 -- Present}}

\colorbox{mygray}{\hspace{0.2em}Ingested advertising streaming data from \textbf{Kafka} into the real-time analytics database \textbf{Druid}.}

\begin{list}{$\bullet$}{\listparam}
\item Exploited Druid's Kafka indexing service and implemented customized Druid row parser to convert source data.  Used \textbf{Jenkins} for unit test, package build and delivery onto Druid cluster.
\item Build an HTTP server in Java to receive metrics emitted by Druid and feed them into \textbf{DataDog}. Utilized Jenkins to create docker image and deployed it on Quantcast \textbf{PAWS} (Kubernates in guise).
\item Deployed the Druid AWS infrastructure as code with \textbf{Terraform}. Wrote bash script for Druid operation.
\end{list}

\subsection{\textbf{Back-end Engineer Intern}\hfill{\textbf{Alibaba, China}}}

{\small\textsl{Taobao Transactoin Platform}}\hfill{{\small 05/10/2018 -- 07/27/2018}}

\colorbox{mygray}{\hspace{0.2em}Built an internal \textbf{Spring Boot} application to automate AI development.}

\begin{list}{$\bullet$}{\listparam}
\item Hooked up offline training platform to other data processing modules.
   \begin{list}{$\circ$}{\sublistparam}
    \item Generated dynamic front-end forms of training parameters for variant algorithms with Google \textbf{Gson}.
    \item Used \textbf{HttpClient} to poll training status, optimistic lock to avoid redundant training trigger.
   \end{list}
\item Delivered trained models to designated client servers with \textbf{Diamond} (config management system) and \textbf{Tair} (distributed cache).
\item Empowered the coupon team to reduce 1 week for tweaking recommendation algorithm.
\end{list}

\subsection{\textbf{Visiting Student\hfill{Singapore University of Technology and Design}}}

{\small\textsl{Natural Language Processing Group, published a paper in IEEE DSAA}}\hfill{{\small 07/13/2016 -- 08/31/2016}}

\colorbox{mygray}{\hspace{0.2em}Ameliorated multi-task deep learning model with \textbf{Keras} for text classification.} 

\begin{list}{$\bullet$}{\listparam}
\item Crawled 75,000 rotten tomato reviews with \textbf{Python}. Set aside CNNs to capture exclusive features and appended gated control unit to filter noise, improving accuracy by 0.47\% and 1.10\% respectively.
\end{list}

\section{PROJECTS}

\subsection{\textbf{Multiplayer Tictactoe with Stream, Multicast and Failover}\hfill{01/2019 -- 04/2019}}

\begin{list}{$\bullet$}{\listparam}
\item Developed the multithreading server in \textbf{C} to monitor game resources and handle various types of requests from multiple clients (New Game, Reoconnect, Move, End) in the TCP thread, process multicasting requests for failover in the UDP thread; Used \textbf{select()} to deal with multitasking.
\item Built the client to multicast for a new server or connect with the backup server while noting that the original server crashes, seamlessly resume the game from last move.
\end{list}

\subsection{\textbf{Selected Side Projects}\hfill{01/2018 -- 06/2019}}

\begin{list}{$\bullet$}{\listparam}
\item \textbf{Lisp Interpreter:} Implemented Lisp interpreter in \textbf{Java} to parse the expression into binary tree, evaluate arguments, bind them to associated formal parameters and recursively evaluate function body.
\item \textbf{Sprint Clone:} Wrote an Sprint clone from scratch in \textbf{Java} and implemented the feature of IoC (Inverse of Control) and AOP (Aspect Oriented Programming).
\item \textbf{Raft:} Implemented the basic raft protocol in \textbf{Go}, including leader election and log replication.
\item \textbf{Seckill Shopping:} Used \textbf{Redis} to reject overselling requests. Combined \textbf{RocketMQ} with local message table to implement the distributed transaction per the choreography-based saga pattern.
\end{list}

\section{PUBLICATION}

Xuanyi Li, Weimin Wu, Hongye Su. Convolutional Neural Networks Based Multi-Task Deep Learning for
Movie Review Classification. In proceedings of the 4th IEEE DSAA. Tokyo, Japan, 10/2017.
\end{document}